Analysis of the included studies

### 2023-06-16 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Updated analysis script with new vaccination modelling category names

```{r}
intervention_categories <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, intervention_type, sort = TRUE) %>% 
  pivot_wider(names_from = intervention_type, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
  adorn_pct_formatting(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
  adorn_ns(... = c('no_vax', 'vax_combination_with_others', 'vax_single'))

@@

```{r}
vax_impact_conclusions <- compact_data_with_citation_keys_no_fmd %>% 
  filter(intervention_type == 'vax_single') %>% 
  count(collab_type, is_vax_effective, sort = T) %>% 
  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
    replace_na(list(yes = 0, n0 = 0, the_outcomes_were_inconclusive = 0)) %>% 
  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_ns(... = c('yes', 'no', 'inconclusive'))

@@

```{r eval=FALSE}
vax_impact_by_disease <- compact_data_with_citation_keys_no_fmd %>% 
  filter(intervention_type == 'vax_single') %>% 
  count(disease, is_vax_effective, sort = T) %>% 
  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
    replace_na(list(yes = 0, no = 0, inconclusive = 0)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_ns(... = c('yes', 'no', 'inconclusive'))

@@

```{r eval=FALSE}
vax_as_single_intervention_studies <- compact_data_with_citation_keys_no_fmd %>% 
  filter(intervention_type == 'vax_single') %>% 
  select(title, disease, bibtexkey, publication_year, intervention_modelled)

@@

```{r}
intervention_categories_fmd <- fmd_data %>% 
  count(collab_type, intervention_type, sort = TRUE) %>% 
  pivot_wider(names_from = intervention_type, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
  adorn_pct_formatting(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
  adorn_ns(... = c('no_vax', 'vax_combination_with_others', 'vax_single'))

@@

```{r}
fmd_vax_impact_conclusions <- fmd_data %>% 
  filter(intervention_type == 'vax_single') %>% 
  count(collab_type, is_vax_effective, sort = T) %>% 
  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
  replace_na(list(no = 0, inconclusive = 0, yes = 0)) %>% 
  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_ns(... = c('yes', 'no', 'inconclusive'))

>>>>

```{r}
intervention_categories <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, intervention_type, sort = TRUE) %>% 
  pivot_wider(names_from = intervention_type, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no_vax', 
                            'vax_as_mixed_intervention', 
                            'vax_compared_to_others')
                    ) %>% 
  adorn_pct_formatting(... = c('no_vax', 
                               'vax_as_mixed_intervention', 
                               'vax_compared_to_others')
                       ) %>% 
  adorn_ns(... = c('no_vax', 
                   'vax_as_mixed_intervention', 
                   'vax_compared_to_others'
                   )
           )

@@

```{r}
vax_impact_conclusions <- compact_data_with_citation_keys_no_fmd %>% 
  filter(intervention_type == 'vax_compared_to_others') %>% 
  count(collab_type, is_vax_effective, sort = TRUE) %>% 
  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
    replace_na(list(yes = 0, n0 = 0, the_outcomes_were_inconclusive = 0)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_ns(... = c('yes', 'no', 'inconclusive'))

@@

```{r eval=FALSE}
vax_impact_by_disease <- compact_data_with_citation_keys_no_fmd %>% 
  filter(intervention_type == 'vax_compared_to_others') %>% 
  count(disease, is_vax_effective, sort = T) %>% 
  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
    replace_na(list(yes = 0, no = 0, inconclusive = 0)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_ns(... = c('yes', 'no', 'inconclusive'))

@@

```{r eval=FALSE}
vax_as_single_intervention_studies <- compact_data_with_citation_keys_no_fmd %>% 
  filter(intervention_type == 'vax_compared_to_others') %>% 
  select(title, author, publication_year, disease, paper_doi, 
         intervention_modelled)

@@

```{r}
intervention_categories_fmd <- fmd_data %>% 
  count(collab_type, intervention_type, sort = TRUE) %>% 
  pivot_wider(names_from = intervention_type, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no_vax', 'vax_as_mixed_intervention', 'vax_compared_to_others')) %>% 
  adorn_pct_formatting(... = c('no_vax', 'vax_as_mixed_intervention', 'vax_compared_to_others')) %>% 
  adorn_ns(... = c('no_vax', 'vax_as_mixed_intervention', 'vax_compared_to_others'))

@@

```{r}
fmd_vax_impact_conclusions <- fmd_data %>% 
  filter(intervention_type == 'vax_compared_to_others') %>% 
  count(collab_type, is_vax_effective, sort = T) %>% 
  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
  replace_na(list(no = 0, inconclusive = 0, yes = 0)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_ns(... = c('yes', 'no', 'inconclusive'))
